---
title: "mapBins"
author: ""
date: "18 October 2021"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold") ## TODO: use 'eval = TRUE'
```

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see https://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library(SpaDES.core)

setPaths(modulePath = file.path("C:/Users/RALAS6/Documents/Repositories/mapBins"))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 1)

parameters <- list(
  #.progress = list(type = "text", interval = 1), # for a progress bar
  ## If there are further modules, each can have its own set of parameters:
  #module1 = list(param1 = value1, param2 = value2),
  #module2 = list(param1 = value1, param2 = value2)
)
modules <- list("mapBins")
objects <- list()
inputs <- list(rasterToMatch = rasterToMatch,
               studyArea = studyArea,
               birdList = birdList,
               birdPreds = birdPreds,
               forestClassRaster = forClassRaster,
               ageRaster = forAgeRaster,
               nonForClassRaster = nonForClassRaster)
outputs <- list("birdPredsRasters")

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

mySimOut <- spades(mySim)

#mySimOut <- simInitAndSpades(times = times, params = parameters, modules = modules, objects = objects)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE}
df_params <- SpaDES.core::moduleParams("mapBins", "C:/Users/RALAS6/Documents/Repositories/mapBins")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("mapBins", "C:/Users/RALAS6/Documents/Repositories/mapBins")` may be sufficient.

```{r moduleInputs, echo = FALSE}
df_inputs <- SpaDES.core::moduleInputs("mapBins", "C:/Users/RALAS6/Documents/Repositories/mapBins")
knitr::kable(df_inputs)
```

Here I fabricate/input some fake data for the testing the module

```{r fabricatedInputs, echo = FALSE}

inputsDir <- checkPath("inputs", create = TRUE)
outputsDir <- checkPath("outputs", create = TRUE)

downloadFolderArea <- checkPath(file.path(inputsDir, "studyArea"), create = TRUE)
downloadFolderForestClass <- checkPath(file.path(inputsDir, "forestClassRasters"), create = TRUE)

#make a birdPred objects

#make a birdList
birdList <- c("OVEN", "CAWA", "BAWW")

#make fake list of birdMatricies 
birdMatricies <- lapply(X = birdList, FUN = function(singleBird){

  landForClass <- rep(1:11, times = 15) 
  ageClasses <- rep(1:15, each = 11) 
  gbmPred <- runif(15*11)
  gbmPredDF<- data.frame(landForClass, gbmPred, ageClasses)
  birdMatrix <- reshape2::acast(gbmPredDF, 
                              landForClass~ageClasses, 
                              value.var= "gbmPred")
  return(birdMatrix)
})
names(birdMatricies) <- birdList


#make fake nonForestedDF
nonforBirdPreds <- lapply(X = birdList, FUN = function(singleBird){

landForClass <- 1:39
meanBirdDensity <- runif(39)
nonForBirdPred <- data.frame(landForClass, meanBirdDensity)
  return(nonForBirdPred)
})
names(nonforBirdPreds) <- birdList

# create table defining age classes
maxAgeClass <- 15
ageGrouping <- 10
maxAge <- 290
allAges <- c(0:maxAge) #make vector counting from 1 to to max age
agesOverMaxAgeClass <- maxAge-(maxAgeClass*ageGrouping) 
ageClasses <- c(1, rep(1:maxAgeClass, each = ageGrouping), rep(maxAgeClass, times = agesOverMaxAgeClass)) #make vector of age classes to correspond with the vector allAges
ageClassDefs <- cbind(allAges,ageClasses) 
ageClassDefs <- as.data.table(ageClassDefs) # put together in ageClassDefs data table
ageClassDefs <- ageClassDefs[, ageClasses:=as.character(ageClasses)] 


#make list object of all module outputs needed for Mapping Module 
birdPreds <- list(birdMatricies, nonforBirdPreds, ageClassDefs) 
names(birdPreds) <- c("birdMatricies", "nonforBirdPreds", "ageClassDefs")



#get rasterToMatch
rasterToMatch <- raster("C:/Users/RALAS6/Documents/Repositories/mapBins/LCC2005_V1_4a.tif")
#rasterToMatch <- LandR::prepInputsLCC(destinationPath = inputsDir) #gets LCC2010

#get studyArea
nameAreaShapefile <- "BCR6_BC.shp" #specify file name
folderUrlArea <- "https://drive.google.com/file/d/1SjUKXOcNqDUkRxRTjwgLlLFjb5LRzbHy"
archiveArea <- "BCR6_BC.zip" #give archive name

studyArea <- prepInputs(targetFile = nameAreaShapefile, 
                        url = folderUrlArea,
                        archive = archiveArea, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderArea, #save the file to a folder in the working directory called studyArea
                        fun = "raster::shapefile", #use the function shapefile
                        targetCRS = crs(rasterToMatch),
                        #rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        overwrite = TRUE,
                        verbose = TRUE)
# studyArea <- spTransform(studyArea, crs(rasterToMatch))

rasterToMatch <- raster::crop(rasterToMatch, studyArea) #create landscapeRaster by cropping rasterToMatch to studyArea
rasterToMatch <- raster::mask(rasterToMatch, studyArea) #mask landscapeRaster to studyArea
#landscapeRasters <- unstack(landscapeRastersStack)

#get forClassRaster

nameForClassRaster <- "VegTypeABBC.tif" #specify file name
folderUrlForClass <- "https://drive.google.com/file/d/1cfrb-RhiwMD4XlS_yzRSQYPVh8ffwC0L/view?usp=sharing"
archiveForClass <- "vegTypeABBC.zip" #give archive name

forClassRaster <- prepInputs(targetFile = nameForClassRaster, 
                        url = folderUrlForClass,
                        archive = archiveForClass, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderForestClass, #save the file to a folder in the working directory called forestClassRasters
                        fun = "raster::raster", #use the function raster
                        #targetCRS = crs(rasterToMatch),
                        rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        studyArea = studyArea,
                        useCache = getOption("reproducible.useCache", FALSE),
                        overwrite = TRUE,
                        verbose = TRUE)

names(forClassRaster) <- c("forClassRaster")

forClassRaster[forClassRaster == 0] <- NA

plot(forClassRaster) #visually check forClassRaster


#get forAgeRaster
nameForAgeRaster <- "ageRas.tif" #specify file name
folderUrlAge <- "https://drive.google.com/file/d/1Ih4YLfIYX6nQcotdd41j4yRtZKRQxYo7/view?usp=sharing"
archiveAge <- "ageRaster.zip" #give archive name

forAgeRaster <- prepInputs(targetFile = nameForAgeRaster, 
                        url = folderUrlAge,
                        archive = archiveAge, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderForestClass, #save the file to a folder in the working directory called forestClassRasters
                        fun = "raster::raster", #use the function raster
                        #targetCRS = crs(rasterToMatch),
                        rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        studyArea = studyArea,
                        overwrite = TRUE,
                        verbose = TRUE)

names(forAgeRaster) <- c("forAgeRaster")

plot(forAgeRaster) #visually check ageRaster


#get nonForRaster
nameNonForRaster <- "LCC2005_V1_4a.tif" #specify file name
folderUrlNonFor <- "https://drive.google.com/file/d/1E3iQRfaSPx0-b2GTgbLZqjo2Nhom39EK/view?usp=sharing"
archiveNonFor <- "LCC2005_V1_4a.zip" #give archive name

nonForRaster <- prepInputs(targetFile = nameNonForRaster, 
                        url = folderUrlNonFor,
                        archive = archiveNonFor, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderForestClass, #save the file to a folder in the working directory called forestClassRasters
                        fun = "raster::raster", #use the function raster
                        #targetCRS = crs(rasterToMatch),
                        rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        studyArea = studyArea,
                        useCache = getOption("reproducible.useCache", FALSE),
                        overwrite = TRUE,
                        verbose = TRUE)

names(nonForRaster) <- c("nonForRaster")

nonForRaster <- overlay(x = nonForRaster, y = forClassRaster, fun = function(x, y) {
                         x[!is.na(y[])] <- NA
                          return(x)
                            })

plot(nonForRaster) #visually check nonForRaster


```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE}
df_outputs <- SpaDES.core::moduleOutputs("mapBins", "C:/Users/RALAS6/Documents/Repositories/mapBins")
knitr::kable(df_outputs)
```

# Links to other modules

Describe any anticipated linkages to other modules.
