---
title: "mapBins"
author: "Isolde Lane Shaw"
date: "10/13/2021"
output: html_document
---

#mapBins Module

Inputs: birdPreds, forestClassRaster, ageRaster, coverClassRaster, studyArea, rasterToMatch 

Outputs: raster of predicted bird density (according to postHocBinning) across the studyArea landscape 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(Require)

#list packages to load
Require("data.table")
Require("rgdal")
Require("sf")
Require("raster")
Require("SpaDES.core") ## TODO: not used
Require("LandR")
Require("googledrive")
Require("plotrix") 
Require("dplyr")
Require("tidyverse")
Require("reshape2")
#Require("tidyr")

inputsDir <- checkPath("inputs", create = TRUE)
outputsDir <- checkPath("outputs", create = TRUE)

downloadFolderArea <- checkPath(file.path(inputsDir, "studyArea"), create = TRUE)
downloadFolderForestClass <- checkPath(file.path(inputsDir, "forestClassRasters"), create = TRUE)
```


# Get Inputs

## Bring in the birdPreds list from postHocBinning

```{r getExampleBirdPreds}

#make fake birdMatrix
landForClass <- rep(1:11, times = 15) 
ageClasses <- rep(1:15, each = 11) 
gbmPred <- runif(15*11)
gbmPredDF<- data.frame(landForClass, gbmPred, ageClasses)
birdMatricies <- reshape2::acast(gbmPredDF, 
                              landForClass~ageClasses, 
                              value.var= "gbmPred")


#make fake nonForestedDF
landForClass <- 1:39
meanBirdDensity <- runif(39)
nonforBirdPreds <- data.frame(landForClass, meanBirdDensity)


# create table defining age classes
maxAgeClass <- 15
ageGrouping <- 10
maxAge <- 290
allAges <- c(0:maxAge) #make vector counting from 1 to to max age
agesOverMaxAgeClass <- maxAge-(maxAgeClass*ageGrouping) 
ageClasses <- c(1, rep(1:maxAgeClass, each = ageGrouping), rep(maxAgeClass, times = agesOverMaxAgeClass)) #make vector of age classes to correspond with the vector allAges
ageClassDefs <- cbind(allAges,ageClasses) 
ageClassDefs <- as.data.table(ageClassDefs) # put together in ageClassDefs data table
ageClassDefs <- ageClassDefs[, ageClasses:=as.character(ageClasses)] 


#make list object of all module outputs needed for Mapping Module 
birdPreds <- list(birdMatricies, nonforBirdPreds, ageClassDefs) 
names(birdPreds) <- c("birdMatricies", "nonforBirdPreds", "ageClassDefs")

```


## Bring in the rasters of forest age and cover type


```{r LCC2005}
rasterToMatch <- raster("C:/Users/RALAS6/Documents/Repositories/mapBins/LCC2005_V1_4a.tif")
#rasterToMatch <- LandR::prepInputsLCC(destinationPath = inputsDir) #gets LCC2010
```



```{r studyArea}
nameAreaShapefile <- "BCR6_BC.shp" #specify file name
folderUrlArea <- "https://drive.google.com/file/d/1SjUKXOcNqDUkRxRTjwgLlLFjb5LRzbHy"
archiveArea <- "BCR6_BC.zip" #give archive name

studyArea <- prepInputs(targetFile = nameAreaShapefile, 
                        url = folderUrlArea,
                        archive = archiveArea, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderArea, #save the file to a folder in the working directory called studyArea
                        fun = "raster::shapefile", #use the function shapefile
                        targetCRS = crs(rasterToMatch),
                        #rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        overwrite = TRUE,
                        verbose = TRUE)
# studyArea <- spTransform(studyArea, crs(rasterToMatch))

rasterToMatch <- raster::crop(rasterToMatch, studyArea) #create landscapeRaster by cropping rasterToMatch to studyArea
rasterToMatch <- raster::mask(rasterToMatch, studyArea) #mask landscapeRaster to studyArea
#landscapeRasters <- unstack(landscapeRastersStack)

```


# Get Landscape Data


```{r getForClassRaster}

nameForClassRaster <- "VegTypeABBC.tif" #specify file name
folderUrlForClass <- "https://drive.google.com/file/d/1cfrb-RhiwMD4XlS_yzRSQYPVh8ffwC0L/view?usp=sharing"
archiveForClass <- "vegTypeABBC.zip" #give archive name

forClassRaster <- prepInputs(targetFile = nameForClassRaster, 
                        url = folderUrlForClass,
                        archive = archiveForClass, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderForestClass, #save the file to a folder in the working directory called forestClassRasters
                        fun = "raster::raster", #use the function raster
                        #targetCRS = crs(rasterToMatch),
                        rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        studyArea = studyArea,
                        useCache = getOption("reproducible.useCache", FALSE),
                        overwrite = TRUE,
                        verbose = TRUE)

names(forClassRaster) <- c("forClassRaster")

forClassRaster[forClassRaster == 0] <- NA

plot(forClassRaster) #visually check forClassRaster

```



```{r getNonForRaster}

nameNonForRaster <- "LCC2005_V1_4a.tif" #specify file name
folderUrlNonFor <- "https://drive.google.com/file/d/1E3iQRfaSPx0-b2GTgbLZqjo2Nhom39EK/view?usp=sharing"
archiveNonFor <- "LCC2005_V1_4a.zip" #give archive name

nonForRaster <- prepInputs(targetFile = nameNonForRaster, 
                        url = folderUrlNonFor,
                        archive = archiveNonFor, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderForestClass, #save the file to a folder in the working directory called forestClassRasters
                        fun = "raster::raster", #use the function raster
                        #targetCRS = crs(rasterToMatch),
                        rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        studyArea = studyArea,
                        useCache = getOption("reproducible.useCache", FALSE),
                        overwrite = TRUE,
                        verbose = TRUE)

names(nonForRaster) <- c("nonForRaster")

nonForRaster <- overlay(x = nonForRaster, y = forClassRaster, fun = function(x, y) {
                         x[!is.na(y[])] <- NA
                          return(x)
                            })

plot(nonForRaster) #visually check nonForRaster

```

```{r getForAgeRaster}

nameForAgeRaster <- "ageRas.tif" #specify file name
folderUrlAge <- "https://drive.google.com/file/d/1Ih4YLfIYX6nQcotdd41j4yRtZKRQxYo7/view?usp=sharing"
archiveAge <- "ageRaster.zip" #give archive name

forAgeRaster <- prepInputs(targetFile = nameForAgeRaster, 
                        url = folderUrlAge,
                        archive = archiveAge, 
                        alsoExtract = "similar", #Extract other files with similar names
                        destinationPath = downloadFolderForestClass, #save the file to a folder in the working directory called forestClassRasters
                        fun = "raster::raster", #use the function raster
                        #targetCRS = crs(rasterToMatch),
                        rasterToMatch = rasterToMatch, #use the specified rasterToMatch to reproject to
                        studyArea = studyArea,
                        overwrite = TRUE,
                        verbose = TRUE)

names(forAgeRaster) <- c("forAgeRaster")

plot(forAgeRaster) #visually check ageRaster
```


#Reclassify the forAgeRaster to ageClassRaster

```{r make ageClassRaster}

#reclassify forAgeRaster into a raster of forest age classes
birdPreds$ageClassDefs <- birdPreds$ageClassDefs[, ageClasses:=as.integer(ageClasses)] #change data type of ageClassDefs
ageClassRaster <- forAgeRaster #make copy of forAgeRaster to be reclassified
ageClassRaster <- reclassify(ageClassRaster, birdPreds$ageClassDefs) #do the reclassification based on ageClassDefs
names(ageClassRaster) <- "ageClassRaster" 
ageClassRaster#check over the raster that has been reclassified
plot(ageClassRaster)

```


# Create new raster of predicted bird densities for the whole studyArea

## 1D mapBins

```{r 1D mapBins}

raster1DBins <- nonForRaster 
raster1DBins <- reclassify(raster1DBins, birdPreds$nonforBirdPreds)
plot(raster1DBins)

```


```{r 2D mapBins}

# check that spatial extent is the same for ageClassraster and forClassraster
extent(forClassRaster) == extent(ageClassRaster)

#reform matrix
matrix <- birdPreds$birdMatricies
reclassTab2D <- melt(matrix)
colnames(reclassTab2D) <- c( "forClass","ageClass", "birdDensityPred")

#reclassify Raster according to reclassTab2D, ageClassRaster and forClassRaster
raster2DBins <- raster(forClassRaster); raster2DBins[] = NA #make an empty NA raster the same as forClassRaster

#make dataframe of all the data in forClassRaster and ageClassRaster and give each cell/row a new definition column, birdDensityPred, from reclassTab2d
f = data.frame(forClass=forClassRaster[], ageClass=ageClassRaster[])
vec = c(1:nrow(f))
f[,3] = vec
m = merge(f, reclassTab2D, all.x=TRUE)
colnames(m)[3] = "ord"
m = m[order(m$ord),]
#populate raster2DBins with the birdDensityPred row of the table m
raster2DBins[] = m$birdDensityPred

#check the new raster
raster2DBins
plot(raster2DBins) 


```


```{r combine 1D and 2D rasters}

birdPredsRaster <- cover(x = raster2DBins,
                         y = raster1DBins,
                         filename = "birdPredsRaster",
                         overwrite = TRUE )

names(birdPreds) <- c("birdpredsRaster")

birdPredsRaster #visually check Raster
plot(birdPredsRaster)

```







